Analysis paper

### 2021-06-02 analysis/analysis.Rmd
add median and sd to tables

  # remove some cols, change column order, sort table and rename horizon
  scores <- scores[, .SD,  .SDcols = !c("coverage_deviation", "rel. skill")]

@@

```{r }
# create scores ----------------------------------------------------------------
# calculate coverage independently and merge with other scores
coverage <- eval_forecasts(
  filtered_data, 
  summarise_by = c("horizon", "model", "target_type", "range"), 
  compute_relative_skill = TRUE, 
  baseline = "Baseline"
)[range %in% c(50, 90), 
                   .(model, target_type, coverage, range, horizon)] %>%
  dcast(formula = ... ~ range, value.var = "coverage")

@@

@@

coverage <- eval_forecasts(
  filtered_data, 
  summarise_by = c("horizon", "model", "target_type", "target_phase", "range"), 
  compute_relative_skill = TRUE, 
  baseline = "Baseline"
)[range %in% c(50, 90), 
                   .(model, target_type, coverage, range, target_phase, horizon)] %>%
  dcast(formula = ... ~ range, value.var = "coverage")

df <- eval_forecasts(
  filtered_data, 
  summarise_by = c("model", "horizon", "target_type", "target_phase"), 
  compute_relative_skill = TRUE, 
  baseline = "Baseline"
) %>%
  merge(coverage, all.x = TRUE, by = c("model", "horizon", "target_phase", "target_type"))

@@

    tmp_df <- df[target_phase == tar & horizon == i, 
                 .(model, interval_score, sharpness,
                   target_phase, horizon,
                   coverage_deviation, relative_skill,  
                   underprediction, overprediction)]

@@

>>>>

  # remove some cols, change column order, sort table and rename horizon
  if (all(c("coverage_deviation", "rel. skill") %in% names(scores))) {
    scores <- scores[, .SD,  .SDcols = !c("coverage_deviation", "rel. skill")]
  }

@@

```{r }
# create scores ----------------------------------------------------------------
# calculate coverage independently and merge with other scores
coverage <- eval_forecasts(
  filtered_data, 
  summarise_by = c("horizon", "model", "target_type", "range"), 
  compute_relative_skill = TRUE, 
  baseline = "Baseline",
)[range %in% c(50, 90), 
                   .(model, target_type, coverage, range, horizon)] %>%
  dcast(formula = ... ~ range, value.var = "coverage")

@@

```{r}
# calculate percentage differences in performance ------------------------------

df <- eval_forecasts(
  filtered_data, 
  summarise_by = c("model", "horizon", "target_type")
)

df <- df %>%
  merge(df[model == "Hub-ensemble", 
           .(horizon, target_type, base_score = interval_score)])
df[, rel_score := (interval_score / base_score) * 100 - 100]
df[, diff_score := interval_score - base_score]
df[, .(horizon, target_type, model, rel_score, diff_score)][order(target_type, horizon)]

@@

coverage <- eval_forecasts(
  filtered_data, 
  summarise_by = c("horizon", "model", "target_type", "target_phase", "range"), 
)[range %in% c(50, 90), 
                   .(model, target_type, coverage, range, target_phase, horizon)] %>%
  dcast(formula = ... ~ range, value.var = "coverage")

df <- eval_forecasts(
  filtered_data, 
  summarise_by = c("model", "horizon", "target_type", "target_phase"), 
  metrics = c("interval_score", "coverage_deviation"),
  sd = TRUE, 
  quantiles = 0.5
) %>%
  merge(coverage, all.x = TRUE, by = c("model", "horizon", "target_phase", "target_type"))

@@

    tmp_df <- df[target_phase == tar & horizon == i, 
                 .(model, interval_score, sharpness,
                   target_phase, horizon, 
                   underprediction, overprediction, 
                   `WIS - median` = interval_score_0.5, 
                   `WIS - sd` = interval_score_sd)]

@@

scores[, .(sd = sd(interval_score)), by = c("model", "target_type")]
